MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-09-14 docs/paper/out/paper.tex
minor fixes in intro -- paper

During the past decade, metagenomics data analysis is growing
exponentially. Some of the reasons behind this are the increasing
throughput of massively parallel sequencing technologies (with the
derived decrease in sequencing costs), and the wide impact of
metagenomics studies \citep{oulas2015metagenomics}, especially in human
health \citep{bikel2015combining}. We should also mention what could be
called the microbiome explosion: all kind of microbiomes (gut, mouth,
skin, urinary tract, airway, milk, bladder) are now routinely sequenced
in different conditions of health and disease, or after different
treatments. The impact of Metagenomics is also being felt in
environmental sciences \citep{ufarte2015discovery}, crop sciences, the
agrifood sector \citep{coughlan2015biotechnological} and biotechnology
in general \citep[\citet{kodzius2015marine}]{cowan2015metagenomics}.
These new possibilities for exploring the diversity of micro--organisms
in the most varied environments are opening new research areas, and
drastically changing the existing ones.

>>>>

During the past decade, metagenomics data analysis is growing
exponentially. Some of the reasons behind this are the increasing
throughput of massively parallel sequencing technologies (with the
derived decrease in sequencing costs), and the wide impact of
metagenomics studies \citep{oulas2015metagenomics}, especially in human
health (diagnostics, treatments, drug response or prevention)
\citep{bikel2015combining}. We should also mention what could be called
the microbiome explosion: all kind of microbiomes (gut, mouth, skin,
urinary tract, airway, milk, bladder) are now routinely sequenced in
different conditions of health and disease, or after different
treatments. The impact of Metagenomics is also being felt in
environmental sciences \citep{ufarte2015discovery}, crop sciences, the
agrifood sector \citep{coughlan2015biotechnological} and biotechnology
in general \citep[\citet{kodzius2015marine}]{cowan2015metagenomics}.
These new possibilities for exploring the diversity of micro--organisms
in the most varied environments are opening new research areas, and
drastically changing the existing ones.
